Python to Assembly Compilation

### 2011-12-12 paper/paper.tex
Create sub sections to visually break up long-blocks-of-fail and add a new section on temp vars

@@

@@

@@

>>>>

\subsubsection{New compiler stages}

@@

\subsubsection{Analysis on when to decrement an object reference}

@@

\subsubsection{Temporary Variables}
The compiler creates temporary variables in a number of situations (namely function calls and as a result of flattened expressions).  These temporary variables need not hang on to their memory reference past the next assignment to the actual result variable.

@@

An additional problem is lack of static single assignment.  When a variable is re-assigned to its own name, the code should decrement the reference counter on the previous version of the object and increment it on the new version.
